Raising the Role of Vocabulary Hubs for Semantic Data Interoperability in Dataspaces

### 2024-06-12 EBDVF-2024/paper.qmd
minor

# Conclusion and Future Work
We presented an approach for dynamically binding dataspace datasets
We have implemented a first prototype of our approach.

>>>>

# Conclusion and Future Work
We presented an approach for dynamically binding datasets to semantic descriptions in a dataspace's Vocabulary Hub,
therefore facilitating data harmonization and easier data consumption.
We have implemented a first prototype of our approach.
